Quantifying the ease of viral escape from broad and narrow antibodies to influenza hemagglutinin

### 2017-10-17 paper/manuscript.tex
Fixed alignment of wildtype sequence in logoplots fig

Despite the similarities in the epitope-targeting of C179 and FI6v3, these two antibodies have very different breadths. FI6v3 can neutralize across many group 1 and group 2 HA's, while C179 can neutralize only some group 1 HA's. The presence of a glycan on the Asn at site 38 in group 2 HA's but not in group 1 HA's has been posited as a reason for this difference in breadth~\citep{corti2011neutralizing, sui2009structural, ekiert2009antibody}. Interestingly, in our experiments, the mutation with the strongest effect size from selection with C179 occurs at site 38, while we do not see observable escape mutations at this site by selection with FI6v3. While the H38S mutation does not introduce a glycosylation motif, we found that HA subtypes susceptible to binding or neutralization by C179 tend to possess a histidine at this site, but subtypes not bound or neutralized by C179 possess a glutamine or serine (Figure~\ref{fig:structures}C).

>>>>

Despite the similarities in the epitope-targeting of C179 and FI6v3, we also see selection for distinct escape mutations with either antibody.
The mutation with the strongest effect size from selection by C179 occurs at site 38, while we do not see observable escape mutations at this site by selection with FI6v3.
Interestingly, we found that HA subtypes susceptible to binding or neutralization by C179 tend to possess a histidine at this site, but subtypes not bound or neutralized by C179 possess a glutamine or serine (Figure~\ref{fig:structures}C). 
This would suggest that susceptibility to neutralization by C179 may in part be determined by the amino-acid identity at site 38.
Furthermore, the difference in breadth between C179 and FI6v3 has been attributed to FI6v3 being able to accommodate a glycan on the Asn at site 38 which is present in group 2 but not group 1 HA's, while group 1-specific stalk-targeting antibodies clash with this glycan~\citep{corti2011neutralizing, sui2009structural, ekiert2009antibody}. 
The H38S mutation selected by C179 does not introduce a glycosylation motif, which indicates that introduction of a glycan at this site is not the only means of mediating escape from this group 1-specific anti-stalk antibody.
